\textbf{ Mapping stellar surfaces\\ II: An interpretable Gaussian process model for light curves }

### 2021-01-25 paper1/ms.tex
DONE

\begin{abstract}
    %
    Thanks to missions like \emph{Kepler} and \emph{TESS}, we now
    have access to tens of thousands of high precision, fast
    cadence, and long baseline stellar photometric observations.
    %
    In principle, these light curves encode a vast amount of information about
    stellar variability and, in particular, about the distribution of
    starspots and other features on their surfaces.
    %
    Unfortunately, the problem of inferring stellar surface properties
    from a rotational light curve is famously ill-posed;
    any inference that relies exclusively on the light curve
    of a single star is \emph{necessarily} prior-dominated.
    %
    The goal of this paper is twofold:
    (1) to explore the various degeneracies affecting the stellar
    light curve ``inversion'' problem and their effect on
    what can and cannot be learned from a stellar surface
    given unresolved photometric measurements; and
    (2) to motivate ensemble analyses of the light curves of
    many stars at once as a powerful method of breaking
    these degeneracies.
    %
    This is the first in a series of papers devoted to the development
    of novel algorithms and tools for the analysis of
    stellar light curves and spectral timeseries, with the
    explicit goal of enabling statistically robust inference
    about their surface properties.
\end{abstract}

@@

\subsection{Implications for inference}
%
It is useful to consider Figure~\ref{fig:nullspace_preimage} in the
context of an inference exercise. One can equivalently think of
the preimage as the solution to a least squares inference problem
in which a completely uninformative prior%
\footnote{%
    More specifically, a zero-mean, infinite variance Gaussian prior on the coefficients of $\mathbf{y}$.
}
is placed on the spherical harmonic
coefficients. In this case, the least squares solution is given by
%
\begin{proof}{test_svd_lstsq}
    \label{eq:inference}
    \hat{\mathbf{y}}
    &=
    \lim_{\lambda \rightarrow 0} \left( \mathbf{A}^\top \mathbf{A} + \lambda \mathbf{I}\right)^{-1} \mathbf{A}^\top \mathbf{f}
    \nonumber\\
    &= \mathbf{y}_\bullet
    \quad.
\end{proof}
%
In this sense, $\mathbf{y}_\bullet$ represents our knowledge about the
surface of a star after an observation if we have no prior information
whatsoever on $\mathbf{y}$.
\emph{Any other information about the surface must come from the prior.}%

@@

\subsection{Dependence on inclination}

@@

Thus far we have focused our discussion on theoretical aspects concerning
what can and cannot be learned from disk-integrated photometric measurements
of stellar surfaces. In this section, we discuss an important degeneracy
introduced by how we actually measure stellar light curves, which we
will refer to as the \emph{baseline degeneracy}.

@@

To summarize, the mean and variance of the ensemble of stellar light curves
in fractional units is
%
\begin{align}
    \mu      & = 1 - c \, n \, \alpha
    \nonumber                         \\
    \sigma^2 & = c^2 \, n \, \beta
    \quad,
\end{align}
%
for some complicated functions $\alpha$ and $\beta$ of the distribution of
stellar inclinations,
rotation periods, and starspot properties.
%
If our observations were collected in these fractional units,
we could uniquely infer the spot contrast $c$ and the number of spots $n$,
since these enter as $c \, n$ and $c^2 n$ in the expressions for the mean
and variance, respectively, and these are straightforward statistics to
compute from the ensemble.
%
However, because of observations are made in \emph{relative} units, in which
we typically normalize to the mean, photometry can only tell us about the \emph{ratio}
%
\begin{align}
    \frac{\sigma}{\mu}
     & \propto \frac{c \sqrt{n}}{1 - c n \alpha}
\end{align}
%
for some value of $\alpha$.
In other words, even photometric ensemble analyses cannot tell
us about the values of the contrast and the number of spots independently.

@@

\xxx{STILL WORKING BELOW.}

\subsection{}

Fortunately, it may be possible to break these degeneracies (at least to some extent)
by collecting photometric data in multiple wavelength bands, an idea that has
been explored recently \citep[e.g.,][]{Gully2017,Guo2018}. Assuming the
locations and sizes of a star's spots are constant in wavelength, the amplitude
of the light curve in different bands (and in particular its slope as a function
of wavelength) can be used to directly constrain the
temperature, and hence the contrast, of the spots. This effectively breaks the
$c-N$ degeneracy. In practice, the effective size of spots may be different
at different wavelengths, which could complicate this picture somewhat. An extension
of the formalism in this paper to multi-band photometry, and a detailed investigation
of the information content of such observations, is left to future work.

\xxx{...}
%

In principle, the maximum level of a light curve could set a lower limit on
the location of the baseline. However, this applies only if the surface is
known to be made up of \emph{exclusively} dark spots. The presence of bright
spots (faculae), which are common on the Sun, make it effectively impossible
for one to infer the baseline from single-band photometry alone.
\citep{Basri2018}.

Recently, \citet{Morris2020} used \emph{Kepler}, \emph{K2}, and \emph{TESS}
light curves to derive a relationship between stellar age and spot
coverage. Because of the intractability of the marginal likelihood function,
that study used an approximate Bayesian computation (ABC) method to
infer spot properties from a large ensemble of stars. \citet{Morris2020}
developed a fast, approximate forward model for light curves of spotted stars
\citep[\textsf{fleck};][]{Morris2020b}, which they used to generate a large
number of prior samples for different values of the spot radii, contrasts,
and latitude distributions. For each collection of samples generated from a
given set of hyperparameters, \citet{Morris2020} computed the distribution of
the ``smoothed amplitude'',
the peak-to-trough difference of the (normalized, de-trended) light curve.
This distribution was then compared to the distribution of observed
smoothed amplitude values among stellar clusters of different ages
within an ABC algorithm, yielding approximate
posterior distributions for the hyperparameters as a function of
stellar age. \citet{Morris2020} found that the spot coverage $f_S$ as a
function of age is well modeled by a simple power law, decreasing from
${\sim}10\%$ for the youngest (${\sim}10$ Myr) stars
to less than $1\%$ for the oldest (${\sim}5$ Gyr) stars.
%
While this broadly agrees with the expectation that stellar
magnetic activity decreases over time, our work strongly suggests
that these results are predominantly prior-dominated. As we discussed
at length
in \S\ref{sec:breaking_baseline_degeneracy} (and found in our inference
runs in \S\ref{sec:calibration-inference}, as well as in the toy
model presented in Figure~\ref{fig:mean_normalization}), the fractional
spot coverage $f_S$ is not an observable in single-band photometry.
%
This is because the expression for $f_S$ (Equation~\ref{eq:fS}) depends on
two quantities: the average spot radius $r$, which we showed can be
constrained, and the total number of spots $n$, which
we showed \emph{cannot} be constrained from single-band light curves.
%
In fact, \citet{Morris2020} assumed $n=3$ for simplicity when doing
posterior inference. We therefore urge care in interpreting those results,
as it is very likely this assumption does not hold across the large
range of spectral types and stellar ages considered in that study.
Nevertheless, the power law scaling of the smoothed amplitude with
age suggests it is still a good metric for stellar ages.

Moreover, the core idea in \citet{Morris2020}
\citep[and in related studies such as][]{Jackson2013}
is very similar
to that advocated here: the use of ensemble analyses to constrain population-level
parameters when invidual datasets are not sufficiently constraining.
Our work builds on that of \citet{Morris2020} by deriving a closed form
solution to the likelihood function (as opposed to a sample-based
likelihood-free inference algorithm) and by harnessing the covariance
structure of the data when doing inference (as opposed to relying solely
on the amplitude of the data).

Another recent paper relevant to our work is that of \citet{Basri2020}, who
investigated the information content of stellar light curves, exploring what
can and cannot be learned about star spot configurations from individual
light curves. That paper strongly urges against the common practice
of interpreting
light curves with one or two dips as originating from one or two spots,
respectively, a point we strongly agree with (c.f. Figure~\ref{fig:degeneracies}).
It also reinforces our point about the additional degeneracies introduced
by the unknown baseline inherent to single-band photometry.
%
Finally, \citet{Basri2020} present a large suite of forward models of light curves of
spotted stars, which they use to discuss the (complicated) dependence of
various light curve metrics on
the physical spot parameters used to generate the data. They conclude that it
is not possible to uniquely relate these metrics to the underlying star spot
configuration. While we agree this is the case for individual stars, our work
stresses that it is possible to break many of these degeneracies with
ensemble analyses.
%
\citet{Basri2020} also conclude it is not in general possible to
uniquely disentangle differential rotation from spot evolution when their
timescales are comparable; nor is it possible to confidently measure a rotation
period when the evolution timescale is very short. However, their study
relies on the effect these processes have on simple light curve metrics,
which are almost certainly not sufficient statistics of the data. Inference
that takes into account the full covariance structure of the data, while
considering large ensembles of light curves, could in principle break
this degeneracy. While we do not explicitly model differential rotation in
this paper, it will be the subject of a future paper in this series.

\xxx{Discuss how this is somewhat similar to what \citet{Rauscher2018} did.}
\xxx{TODO...}

Nevertheless, it is still possible to uniquely and precisely infer the spot properties
under limb darkening,
but as a rule of thumb, the stronger the limb darkening, the larger the
ensemble must be.

>>>>

\begin{abstract}
    %
    Thanks to missions like \emph{Kepler} and \emph{TESS}, we now
    have access to tens of thousands of high precision, fast
    cadence, and long baseline stellar photometric observations.
    %
    In principle, these light curves encode a vast amount of information about
    stellar variability and, in particular, about the distribution of
    starspots and other features on their surfaces.
    %
    Unfortunately, the problem of inferring stellar surface properties
    from a rotational light curve is famously ill-posed;
    any inference that relies exclusively on the light curve
    of a single star is \emph{necessarily} prior-dominated.
    %
    The goal of this paper is twofold:
    (1) to explore the various degeneracies affecting the stellar
    light curve ``inversion'' problem and their effect on
    what can and cannot be learned from a stellar surface
    given unresolved photometric measurements; and
    (2) to motivate ensemble analyses of the light curves of
    many stars at once as a powerful method of breaking
    these degeneracies.
    %
    This is the first in a series of papers devoted to the development
    of novel algorithms and tools for the analysis of
    stellar light curves and spectral time series, with the
    explicit goal of enabling statistically robust inference
    about their surface properties.
\end{abstract}

@@

\subsection{Implications for inference}
%
The procedure we carried out in the previous section is similar to what was done in \citet{Rauscher2018}
for eclipse mapping of exoplanets. That work decomposed the surface map
using principal component analysis (PCA), finding an orthogonal set of
light curve signals and their corresponding surface modes (the left and right
singular vectors in SVD, respectively). Inference was then carried out in
the basis spanned by the components in the preimage, which can be uniquely
constrained by the data.

Let us therefore consider Figure~\ref{fig:nullspace_preimage} in the
context of an inference exercise. One can equivalently think of
the preimage as the solution to a least squares inference problem
in which a completely uninformative prior%
\footnote{%
    More specifically, a zero-mean, infinite variance Gaussian prior on the coefficients of $\mathbf{y}$.
}
is placed on the spherical harmonic
coefficients. In this case, the least squares solution is given by
%
\begin{proof}{test_svd_lstsq}
    \label{eq:inference}
    \hat{\mathbf{y}}
    &=
    \lim_{\lambda \rightarrow 0} \left( \mathbf{A}^\top \mathbf{A} + \lambda \mathbf{I}\right)^{-1} \mathbf{A}^\top \mathbf{f}
    \nonumber\\
    &= \mathbf{y}_\bullet
    \quad.
\end{proof}
%
In this sense, $\mathbf{y}_\bullet$ represents our knowledge about the
surface of a star after an observation if we have no prior information
whatsoever on $\mathbf{y}$.
\emph{Any other information about the surface must come from the prior.}%

@@

\subsection{Dependence on inclination}
\label{sec:inclination}

@@

Thus far we have focused our discussion on theoretical aspects concerning
what can and cannot be learned from disk-integrated photometric measurements
of stellar surfaces. In this section, we discuss an important degeneracy
introduced by how we actually measure stellar light curves, which we
will refer to as the \emph{baseline degeneracy}. This degeneracy has been
pointed out before \citep[e.g.,][]{Basri2018}, but it is useful to revisit and
build on it here.

@@

To summarize, the mean and variance of the ensemble of stellar light curves
in fractional units is
%
\begin{align}
    \mu      & = 1 - c \, n \, \alpha
    \nonumber                         \\
    \sigma^2 & = c^2 \, n \, \beta
    \quad,
\end{align}
%
for some complicated functions $\alpha$ and $\beta$ of the distribution of
stellar inclinations,
rotation periods, and starspot properties.
%
If our observations were collected in these fractional units,
we could uniquely infer the spot contrast $c$ and the number of spots $n$,
since these enter as $c \, n$ and $c^2 n$ in the expressions for the mean
and variance, respectively, and these are straightforward statistics to
compute from the ensemble.
%
However, because of observations are made in \emph{relative} units, in which
we typically normalize to the mean, photometry can only tell us about the \emph{ratio}
%
\begin{align}
    \label{eq:ratio}
    \frac{\sigma}{\mu}
     & \propto \frac{c \sqrt{n}}{1 - c n \alpha}
\end{align}
%
for some value of $\alpha$.
In other words, even photometric ensemble analyses cannot tell
us about the values of the contrast and the number of spots independently.

@@

\subsection{Degeneracies stemming from the null space}

In this paper we explored various degeneracies in the problem of
inferring a stellar surface map from its rotational light curve.
We discussed the idea behind the null space, the set of surface modes that
have exactly zero effect on the observed light curve (\S\ref{sec:nullspace}).
For rotational light curves, we showed that the vast majority of the information
about the surface intensity is in the null space and therefore cannot
be inferred from unresolved photometric measurements. We showed, in particular,
that the size of the null space grows \emph{quadratically} with increasing spatial
resolution, while the number of signals one can infer from a light curve
only grow \emph{linearly}. Consequently, the information content of light
curves is small for large scale surface features and \emph{vanishingly small}
for small scale features.

A direct consequence of this fact is that results based on analyses
of individual light curves are necessarily prior-dominated; i.e.,
the results are extremely sensitive to
the particular assumptions of one's model. We therefore urge lots of care
in these kinds of analyses, where assumptions of uniform-contrast, discrete, and
circular spots, or maximum entropy or ``simplicity'' assumptions may
result in significant bias. In this respect, we agree with the recent
paper by \citep{Basri2020}, which cautions against the association of
invidual dips in light curves with individual, discrete spots.

One of the main results in this paper concerning the null space is its
dependence on stellar inclination (\S\ref{sec:inclination}). Because the modes that lie in the null
space change depending on the viewing angle, observations of a star at many
inclinations break many of the degeneracies in the mapping problem. While
this is obviously infeasible in practice, the dependence of the null
space on inclination motivates ensemble analyses of many similar stars
as a way of circumventing the mapping degeneracies. As we show in
\citetalias{PaperII} in this series, the joint analysis of tens to hundreds
of light curves can uniquely constrain the distribution of starspot
sizes and latitudes among the stars in the sample. In that paper,
we show that ensemble analyses can
even break the latitude-inclination degeneracy \citep[e.g.,][]{Walkowicz2013},
allowing one to infer individual stellar inclinations, typically to within
about $10^\circ$.

We also showed how the null space is a strong function of the stellar limb
darkening. While this can again be used to our advantage---by harnessing the
variance in the limb darkening parameters across an ensemble of stellar
light curves---in practice it is likely to complicate inference, since
any bias in the assumed limb darkening coefficients will likely result in
bias in the inferred surface properties. We revisit this point in
\citetalias{PaperII}.

One final point that we did not address thus far concerns occultations.
Our results regarding the null space apply strictly to rotational light curves,
in which all points on the projected disk contribute to the measured flux.
During an occultation by a transiting planet or a binary companion, the
weighting of surface modes giving rise to the light curve changes
substantially. In fact, the presence of an occultor breaks many of the perfect
symmetries that give rise to a null space in the first place
\citep[e.g.,][]{Luger2019}. This fact can be used to infer the properties
of spots in the path of the occultor, as was done (for example)
by \citet[e.g.,][]{Morris2017}. A detailed investigation of the null space
for the occultation problem is beyond the scope of this work.

\subsection{Degeneracies due to the unknown baseline}

The second major source of degeneracies is the fundamental
unknowability of the true baseline level in single-band
photometry (\S\ref{sec:baseline}), which is summarized in
Figure~\ref{fig:mean_normalization}. In a nutshell, the relationship
between the amplitude of a feature in the light curve and the contrast
of the feature that gave rise to it depends on quantities like the
unspotted photospheric brightness, which is not an observable in
single-band photometry. This leads to the possibility of distinctly
different stellar surfaces having identical \emph{relative}
light curves, as demonstrated in the figure.

In practice, this degeneracy usually manifests as a nonlinear correlation
between the contrast $c$ of a spot and the total number $n$
of spots on the surface of the star. Even in ensemble analyses,
one cannot in general learn these two quantities independently,
only a (complicated) function of the two (Equation~\ref{eq:ratio}).
%
A direct consequence of this degeneracy is that \textbf{it is not in general
    possible to uniquely constrain the total spot coverage of
    a star from single-band light curves.}

Recently, \citet{Morris2020} performed an ensemble analysis of
\emph{Kepler}, \emph{K2}, and \emph{TESS}
light curves to derive a relationship between the fractional spot
coverage $f_S$ and stellar age.
%
% That work inferred a power-law
% scaling between the fractional
% ``smoothed amplitude'',
% the peak-to-trough difference of the (normalized, de-trended) light curve,
% and the fractional spot coverage $f_S$
% This distribution was then compared to the distribution of observed
% smoothed amplitude values among stellar clusters of different ages
% within an ABC algorithm, yielding approximate
% posterior distributions for the hyperparameters as a function of
% stellar age.
That work found that the spot coverage $f_S$ as a
function of age is well modeled by a simple power law, decreasing from
${\sim}10\%$ for the youngest (${\sim}10$ Myr) stars
to less than $1\%$ for the oldest (${\sim}5$ Gyr) stars.
%
While this broadly agrees with the expectation that stellar
magnetic activity decreases over time, our work strongly suggests
that these results are predominantly prior-dominated.
%
This is because the expression for $f_S$ (Equation~\ref{eq:fS}) depends on
two quantities: the average spot radius $r$, which can be
constrained \citep[see][]{PaperII}, and the total number of spots $n$, which
we showed \emph{cannot} be constrained from single-band light curves.
%
In fact, \citet{Morris2020} assumed $n=3$ for simplicity when doing
posterior inference. We therefore urge care in interpreting those results,
as it is very likely this assumption does not hold across the large
range of spectral types and stellar ages considered in that study.
%
Nevertheless, the other central result of that paper, the relationship
between the ``smoothed amplitude'' of a light curve and the stellar age,
\emph{is} valid.
%
Moreover, the core idea in \citet{Morris2020}
\citep[and in related studies such as][]{Jackson2013}
is very similar
to that advocated here: the use of ensemble analyses to constrain population-level
parameters when invidual datasets are not sufficiently constraining.

Another recent paper relevant to our work is that of \citet{Basri2020}, who
investigated the information content of stellar light curves, exploring what
can and cannot be learned about star spot configurations from individual
light curves. That paper strongly urges against the common practice
of interpreting
light curves with one or two dips as originating from one or two spots,
respectively, a point we strongly agree with (c.f. our Figure~\ref{fig:degeneracies}).
It also reinforces our point about the additional degeneracies introduced
by the unknown baseline inherent to single-band photometry.
%

% SOLUTIONS TO BASELINE DEGENERACY

As with the degeneracies due to the null space, there are potential ways
to break the baseline degeneracy.
%
In principle, the maximum level of a light curve could set a lower limit on
the location of the baseline (or, equivalently, the brightness of the
unspotted photosphere), particularly for long-baseline, time-variable
surfaces \citep{Basri2018}. However, this would work only if the surface is
known to be made up \emph{exclusively} of dark spots. The presence of bright
spots (faculae), which are common on the Sun, make it difficult
for one to infer the baseline from single-band photometry in practice.

A better approach may be to collect photometric data in
multiple wavelength bands, an idea that has
been explored recently \citep[e.g.,][]{Gully2017,Guo2018}. Assuming the
locations and sizes of a star's spots are constant in wavelength, the amplitude
of the light curve in different bands (and in particular its slope as a function
of wavelength) can be used to directly constrain the
temperature, and hence the contrast, of the spots. This effectively breaks the
$c-N$ degeneracy. In practice, the effective size of spots may be different
at different wavelengths, which could complicate this picture somewhat, but
the point still stands that light curves collected in multiple bands
contain at least \emph{partial} information about the baseline.
%
A more detailed analysis of the information content of multi-band light curves,
and, by extension, spectroscopic timeseries, is deferred to a future paper
in this series.

\subsection{Future work}

This paper is the first in a series dedicated to developing
methodology to infer stellar surface properties from light curves
and spectroscopic timeseries. It sets the stage for \citet{PaperII},
in which we develop an interpretable Gaussian process (GP) model for
starspot-induced light curve variability. This GP is aimed specifically
at the difficult problem of jointly modeling many light curves
in an ensemble analysis. Although we hinted at this here, we will show
in that paper that ensemble analyses can uniquely constrain several
statistical properties of starspots, including their distribution
of radii and latitudes across stars in the ensemble. In that work
we also consider temporally evolving surfaces, which we neglected
in our discussion thus far.

\vspace{2em}

In keeping with other papers in the \starry series, all figures in this
paper are generated automatically from open-source scripts linked to in
each of the captions \codeicon, and the principal equations link to associated
unit tests that ensure the accuracy and reproducibility of the algorithm
presented here \testpassicon/\testfailicon.

%
%
%
%
%
%
%
%

\vspace{2em}

We would like to thank Michael Gully-Santiago and the
Astronomical Data Group at the Center for Computational Astrophysics for
many thought-provoking discussions that helped shape this paper.

### 2021-01-25 paper2/ms.tex
DONE

\xxx{Similar to \citet{Morris2020}}.

>>>>

\xxx{Similar to \citet{Morris2020}}.
Our work builds on that of \citet{Morris2020} by deriving a closed form
solution to the likelihood function (as opposed to a sample-based
likelihood-free inference algorithm) and by harnessing the covariance
structure of the data when doing inference (as opposed to relying solely
on the amplitude of the data).

Recently, \citet{Morris2020} used \emph{Kepler}, \emph{K2}, and \emph{TESS}
light curves to derive a relationship between stellar age and spot
coverage. Because of the intractability of the marginal likelihood function,
that study used an approximate Bayesian computation (ABC) method to
infer spot properties from a large ensemble of stars. \citet{Morris2020}
developed a fast, approximate forward model for light curves of spotted stars
\citep[\textsf{fleck};][]{Morris2020b}, which they used to generate a large
number of prior samples for different values of the spot radii, contrasts,
and latitude distributions. For each collection of samples generated from a
given set of hyperparameters, \citet{Morris2020} computed the distribution of
the ``smoothed amplitude'',
the peak-to-trough difference of the (normalized, de-trended) light curve.
This distribution was then compared to the distribution of observed
smoothed amplitude values among stellar clusters of different ages
within an ABC algorithm, yielding approximate
posterior distributions for the hyperparameters as a function of
stellar age. \citet{Morris2020} found that the spot coverage $f_S$ as a
function of age is well modeled by a simple power law, decreasing from
${\sim}10\%$ for the youngest (${\sim}10$ Myr) stars
to less than $1\%$ for the oldest (${\sim}5$ Gyr) stars.
%
While this broadly agrees with the expectation that stellar
magnetic activity decreases over time, our work strongly suggests
that these results are predominantly prior-dominated. As we discussed
in \S\ref{sec:baseline}, the fractional
spot coverage $f_S$ is not an observable in single-band photometry.
%
This is because the expression for $f_S$ (Equation~\ref{eq:fS}) depends on
two quantities: the average spot radius $r$, which we showed can be
constrained, and the total number of spots $n$, which
we showed \emph{cannot} be constrained from single-band light curves.
%
In fact, \citet{Morris2020} assumed $n=3$ for simplicity when doing
posterior inference. We therefore urge care in interpreting those results,
as it is very likely this assumption does not hold across the large
range of spectral types and stellar ages considered in that study.
Nevertheless, the power law scaling of the smoothed amplitude with
age suggests it is still a good metric for stellar ages.

\xxx{Basri:}
Finally, \citet{Basri2020} present a large suite of forward models of light curves of
spotted stars, which they use to discuss the (complicated) dependence of
various light curve metrics on
the physical spot parameters used to generate the data. They conclude that it
is not possible to uniquely relate these metrics to the underlying star spot
configuration. While we agree this is the case for individual stars, our work
stresses that it is possible to break many of these degeneracies with
ensemble analyses.
%
\citet{Basri2020} also conclude it is not in general possible to
uniquely disentangle differential rotation from spot evolution when their
timescales are comparable; nor is it possible to confidently measure a rotation
period when the evolution timescale is very short. However, their study
relies on the effect these processes have on simple light curve metrics,
which are almost certainly not sufficient statistics of the data. Inference
that takes into account the full covariance structure of the data, while
considering large ensembles of light curves, could in principle break
this degeneracy. While we do not explicitly model differential rotation in
this paper, it will be the subject of a future paper in this series.
